Covariate analysis of CMC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (ACC and DLPFC with CQN normlaisation)

### 2017-07-29 code/Rmd/CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN.Rmd

knit2synapse::knitToFolderEntity(file = "./CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN.Rmd",
                                 parentId = "syn7501880",
                                 entityName = 'ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = "syn7501880";
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of STAR aligned feature counts with Ensembl v75 with CQN normalisation (ACC and DLPFC)';

>>>>

knit2synapse::knitToFolderEntity(file = "./CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN.Rmd",
                                 parentId = "syn9872607",
                                 entityName = 'ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = "syn9872607";
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of STAR aligned feature counts with Ensembl v75 with CQN normalisation (ACC and DLPFC)';

### 2017-07-29 code/Rmd/CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_MSSM.Rmd

knit2synapse::knitToFolderEntity(file = "./CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN.Rmd",
                                 parentId = "syn9872607",
                                 entityName = 'ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = "syn9872607";
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of STAR aligned feature counts with Ensembl v75 with CQN normalisation (ACC and DLPFC)';

thisFileName <- 'CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN.Rmd'

@@

METADATA = rbindlist(list(METADATA_ACC, METADATA_DLPFC), use.names = T, fill = T) %>%
  droplevels() %>%
  list(.,METADATA_QC) %>%
  join_all %>%
  dplyr::mutate(LibraryBatch = as.factor(LibraryBatch)) %>%
  left_join(ANCESTRY) %>%
  unique

@@

### Covariates clustering
Determine relationship between covariates. 
```{r covariates.clustering}
FactorCovariates <- c('Individual_ID', "Institution", "Gender", "LibraryBatch", "Dx.Tissue", "RibozeroBatch", "FlowcellBatch")
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate",
                    "GenesDetected", "TranscriptsDetected", "ExpProfEfficiency", "rRNARate", "TotalReads", 
                    "PercentAligned", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")

@@

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preAdjustedSigCovars.NULL, fig.width=20, fig.height=12}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```
### Normalisation
Based on different model selection methodology (as seen here syn8468116, syn9772932, and syn9774491), following variables are used as covariates: Institution, Gender, RIN, and IntronicRate

@@

```{r custom.normalisation, results='asis'}
# Primary variable of interest
postAdjustCovars = c('Dx.Tissue', 'Institution', 'Gender', 'RIN', 'IntronicRate')

@@

  normalizationType	= 'CQN'
)

# Code
CODE <- Folder(name = "ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)

>>>>

knit2synapse::knitToFolderEntity(file = "./CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_MSSM.Rmd",
                                 parentId = "syn7501880",
                                 entityName = 'ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - MSSM')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = "syn7501880";
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of STAR aligned feature counts with Ensembl v75 with CQN normalisation (ACC and DLPFC)';

thisFileName <- 'CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_MSSM.Rmd'

@@

METADATA = rbindlist(list(METADATA_ACC, METADATA_DLPFC), use.names = T, fill = T) %>%
  droplevels() %>%
  list(.,METADATA_QC) %>%
  join_all %>%
  dplyr::mutate(LibraryBatch = as.factor(LibraryBatch)) %>%
  left_join(ANCESTRY) %>%
  dplyr::filter(Institution == 'MSSM') %>%
  unique

@@

### Covariates clustering
Determine relationship between covariates. 
```{r covariates.clustering}
FactorCovariates <- c("Individual_ID", "Gender", "LibraryBatch", "Dx.Tissue", "RibozeroBatch", "FlowcellBatch")
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate",
                    "GenesDetected", "TranscriptsDetected", "ExpProfEfficiency", "rRNARate", "TotalReads", 
                    "PercentAligned", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")

@@

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preAdjustedSigCovars.NULL, fig.width=20, fig.height=12}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```
### Normalisation
Based on different model selection methodology (as seen here syn8468116, syn9772932, and syn9774491), following variables are used as covariates: Gender, RIN, and IntronicRate

@@

```{r custom.normalisation, results='asis'}
# Primary variable of interest
postAdjustCovars = c('Dx.Tissue', 'Gender', 'RIN', 'IntronicRate')

@@

  normalizationType	= 'CQN',
  institution = 'MSSM'
)

# Code
CODE <- Folder(name = "ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - MSSM", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)
